Conformance Checking Using Embeddings and the Applicability of Such Methods in the Internet of Things

### 2021-11-29 paper.tex
Discussion

\begin{document}
%
\title{Seminar Paper}
\subtitle{Seminar Business Processes and the Internet of Things \\ Conformance Checking Using Activity and Trace Embeddings.}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Kruska \\ Supervisor: Dr. István Koren}
%
\authorrunning{Jan Kruska}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany}
%	\email{jan.kruska@rwth-aachen.de}\\
%	\url{http://www.pads.rwth-aachen.de/}}
%
\maketitle              % typeset the header of the contribution
%
%
%
%
%\section{Planned structure}
%The following list shall give a short overview of the intended general structure of the seminar paper. For each section the main questions that should be answered by it are listed.
%\begin{enumerate}
%	\item Abstract
%	\item Introduction
%	\begin{enumerate}
%		\item What is the motivation of the paper
%	\end{enumerate}
%	\item Background
%	\begin{enumerate}
%		\item What is conformance checking, how is it useful and why would you do it, which methods are there, what are advantages and disadvantages of said methods.
%		\item What is NLP (briefly), what are embeddings generally and word embeddings specifically, what are word2vec and doc2vec and how do they approach the NLP problems.
%		\item What parallels are there between NLP and conformance checking
%		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
%		\item What is the Internet of Things and why would one wish to perform process analysis there
%	\end{enumerate}
%	\item Method
%	\begin{enumerate}
%		\item How were word2vec and doc2vec adapted to conformance checking in the paper (I.e. practical adaption)
%	\end{enumerate}
%	\item Results
%	\begin{enumerate}
%		\item What are the results given in the paper
%		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one chosen, what advantages or disadvantages do different metrics have.
%		\item What are the results when using their code and reproducing the results (ideally the same)
%	\end{enumerate}
%	\item Outlook
%	\begin{enumerate}
%		\item What future work do the authors suggest
%		\item What problems were encountered when trying to reproduce the results from the paper. Could they be reproduced completely, just in part or not at all? If so, are there suggestions on how could these problems be mitigated.
%	\end{enumerate}
%\end{enumerate}

@@

First an activity embeddings for the log were trained, which then allows for the comparison of two traces by comparing their individual activities in the embedding space.
Given some similarity metric and the real log as well as the model log a dissimilarity matrix can be built up.
From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e. $a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well fitting one.
As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
Conversely each row contains all similarities between a trace in the model log and all traces in the real log.
A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.

@@

To evaluate the suitability of the method three sets of experiments were performed. 
The first set of experiments focussed on the scalability of the approach, the second aimed to assess the the effect of applying noise to a log and comparing that to the noiseless log.
The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
This was achieved by generating 1000 traces from a randomly generated process tree, which form the real log.
Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1 and the ILP Miner were selected as discovery algorithms.
Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms aswell as the method described in the paper.

@@

>>>>

\begin{document}
%
\title{Conformance Checking Using Embeddings and the Applicability of Such Methods in the Internet of Things}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Kruska}
%
\authorrunning{Jan Kruska}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany}
%	\email{jan.kruska@rwth-aachen.de}\\
%	\url{http://www.pads.rwth-aachen.de/}}
%
\maketitle              % typeset the header of the contribution
%
%
%
%
%\section{Planned structure}
%The following list shall give a short overview of the intended general structure of the seminar paper. For each section the main questions that should be answered by it are listed.
%\begin{enumerate}
%	\item Abstract
%	\item Introduction
%	\begin{enumerate}
%		\item What is the motivation of the paper
%	\end{enumerate}
%	\item Background
%	\begin{enumerate}
%		\item What is conformance checking, how is it useful and why would you do it, which methods are there, what are advantages and disadvantages of said methods.
%		\item What is NLP (briefly), what are embeddings generally and word embeddings specifically, what are word2vec and doc2vec and how do they approach the NLP problems.
%		\item What parallels are there between NLP and conformance checking
%		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
%		\item What is the Internet of Things and why would one wish to perform process analysis there
%	\end{enumerate}
%	\item Method
%	\begin{enumerate}
%		\item How were word2vec and doc2vec adapted to conformance checking in the paper (I.e. practical adaption)
%	\end{enumerate}
%	\item Results
%	\begin{enumerate}
%		\item What are the results given in the paper
%		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one chosen, what advantages or disadvantages do different metrics have.
%		\item What are the results when using their code and reproducing the results (ideally the same)
%	\end{enumerate}
%	\item Outlook
%	\begin{enumerate}
%		\item What future work do the authors suggest
%		\item What problems were encountered when trying to reproduce the results from the paper. Could they be reproduced completely, just in part or not at all? If so, are there suggestions on how could these problems be mitigated.
%	\end{enumerate}
%\end{enumerate}

@@

First an activity embeddings for the log were trained, which then allows for the comparison of two traces by comparing their individual activities in the embedding space.
Given some similarity metric and the real log as well as the model log a dissimilarity matrix can be built up.
From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e. $a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well fitting one.
As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.

@@

To evaluate the suitability of the method three sets of experiments were performed. 
The first set of experiments focussed on the scalability of the approach, especially since more traditional approaches do not scale well. This aspect is doubly important when talking about the Internet of Things, where computing resources are generally far more constrained, while still producing large amounts of event data.

The second set of experiments aimed to determine whether the method responded as expected when providing noisy logs.
These experiments were designed to verify the soundness of approach.
This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs and determining the conformance between the noiseless and noisy logs.
The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.

The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
This was achieved by generating 1000 traces from a randomly generated process tree, which form the real log.
Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1 and the ILP Miner were selected as discovery algorithms.
Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms as well as the method described in the paper.

@@

Peeperkorn et al. obtained promising first results for a novel bedding based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation are the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases and also to systematically broaden the parameters for random process tree generation to cover more different classes.

%Secondly the sizes of the process logs for the scalability experiment were between 100 to 5000 traces, the log sizes for the noise and discovery experiment were fixed at 1000 traces.

Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
A thorough investigation into the effect of these parameters should follow, since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.

Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an orderless bag of words.
At least from an intuitive understanding of conformance checking order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.

Lastly the paper should be understood as a first stepping stone for the use of NLP-related algorithms for the task of conformance checking.
The use of embeddings is often a first step in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
As such further research into the applicability of a variety of other methods could be fruitful.
The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation and recurrent neural networks.
